---
title: "HW1_1.42"
author: "Gehua Zhang (UNI:gz2280)"
date: '2018-09-16'
output:
  pdf_document: default
  html_document: default
---

## 1.42
####a.

$$
\frac{1}{(32\pi)^{3}}exp(-\frac{1}{32}\Sigma_{i=1}^{n}(Y_{i}-\beta{1}X_{i})^2)
$$


####b.
First we define the likelihood funtion

```{r}
likelihood = function(xList, yList, sigma, beta1) {
  value = 1
  for (i in 1:length(xList))
  {
    value = value * 1/(sqrt(2*pi)*sigma) * exp(-1/2*(yList[i]-beta1*xList[i])^2/(sigma^2))
  }
  return(value)
}
```
Then we calculate coresponding $\beta_{1}=17,18,19$
```{r}
xList <- c(7,12,4,14,25,30)
yList <- c(128,213,75,250,446,540)

likelihood(xList, yList, 4, 17)
likelihood(xList, yList, 4, 18)
likelihood(xList, yList, 4, 19)
```

####c.
We define Maximum Likelihood function based on the formula it provides:
```{r}
maxLikelihood <- function(xList,yList){
  value = sum(xList*yList)/sum(xList^2)
  return(value)
}
maxLikelihood(xList,yList)
```
It is consistent with our result in part b, which we obtain maximum likelihood around $\beta_{1}=18$

####d.
We make a list of $\beta_{1}$ from 17 to 19 by increment 0.01
```{r}
beta1 <- seq(17, 19, by=0.01)
likeList = likelihood(xList,yList,4,beta1)
plot(beta1,likeList)
```


The plot clearly shows that a point slightly aleft 18.0 which obtains the maximum likelihood function.




