---
title: "GR_5205 HW_2"
author: "Gehua Zhang (UNI:gz2280)"
date: "9/22/2018"
output:
  pdf_document: default
  html_document: default
---

***

#### 2.1.a

This conclusion is not warranted.
$$
H_0: \beta_1 = 0 \\
H_1: \beta_1 \neq 0
$$


For both intercept and slope lay inside confidence interval:
$$
\beta_0^* = 7.43119 \in [-1.18518, 16.0476] \\
\beta_1^* = 0.755048 \in [0.452886, 1.05721]
$$
Which implies we concluded null hypothesis that there is no linear relationship between sales and population.

Level of significance: $\alpha = 5 \%$



#### 2.1.b

This interval could be negative, due to the possibilities that our $t$ value could be large:
In this case, degree of freedom = 48, with 95% confidence interval, 

```{r}
qt(0.975,48)
```
t(0.975;48) = 2.010635

For the confidence interval,

$$
b_1 \pm t(1-\alpha/2;n-2)*s(b_1)
$$
If we have a relative large t value and small $b_1$, it is possible to obtain a negative limit.

From a real life perspective to interpret this negative boundary, we just choose a strict level of significance thus our model over-protects us from the majority of circumstances (where sales$>0$), and even some impossible situations (sales$<0$). The model derives from a mathematical view to ensure that our interval is safety enough so it is not weird to have negative values.


***

#### 2.2

If we concluded $H_0:\beta_1 \leq 0$, which implies there is a non-postive relation of $X$ and $Y$, but we are not sure if $\beta_1 = 0$. We should have a further test that $H_0:\beta_1=0$ and $H_1: \beta_1 \neq 0$ to make sure if there is a linear association between $X$ and $Y$.


***

#### 2.3
Since it is a test of slope, we assume the hypothesis should be:

$$
H_0:\beta_1 = 0
\\
H_1:\beta_2 \neq  0
$$
And we obtain a p-value $= 0.91$.

From the definition of p-value, it is the smallest $\alpha$ which rejects our null hypothesis. So here the smallest $\alpha = 0.91$, which implies that we only have 19% confidence interval to reject null hypothesis, that is, we have a weak evidence to reject null hypothesis, thus we conclude null hypothesis. In this case, we conclude that there may be no association of $X$ and $Y$, the student is wrong.


***

#### 2.4.a

```{r}
data<-read.table("/Users/gehuazhang/Desktop/Data\ Sets/Chapter\ \ 1\ Data\ Sets/CH01PR19.txt")
colnames(data)<-c("GPA","ACT")
fit<-lm(data$GPA~data$ACT)
fit
```

```{r}
slopeTwoSideCI <- function(xList, yList, alpha){
  fit <- lm(yList~xList)
  b1 <- summary(fit)$coefficients[2,1]
  s_b1 <- summary(fit)$coefficients[2,2]
  n <- length(xList)
  t_value <- qt(1-alpha/2,length(yList)-2)
  t_star <- b1/s_b1
  interval <- c(b1-t_value*s_b1, b1+t_value*s_b1)
  names(interval)<-c("confidence interval","confidence interval")
  return(c(t_star,interval))
}

slopeTwoSideCI(data$ACT,data$GPA,0.01)[2:3]
```

The confidence of $\beta_1$ does not include zero. Admission director is interested about zero because this telling he/she that students' GPA may not correspond to their ACT scores.

#### 2.4.b
Hypothesis:
$$
H_0:\beta_1 = 0
\\
H_1:\beta_1 \neq 0
$$
```{r}
t_star <- slopeTwoSideCI(data$ACT,data$GPA,0.01)[1]
names(t_star)<-"t*"
t_star
t_value <- qt(1-0.01/2,length(data$GPA)-2)
names(t_value)<-"t_value"
t_value
```


$$
b_1 = 0.03883
\\
\\
t^* = \frac{b_1}{s(b_1)} = 3.039777
\\
t(1-\alpha/2;n-2) = 2.618137
$$
Since $|t^*| > t(1-\alpha/2;n-2)$, we should reject our null hypothesis and conclude that there is association for students' ACT and GPA.

#### 2.4.c

```{r}
p_value <- 2*pt(3.039777, length(data$GPA)-2, lower=FALSE)
p_value
```
Since p-value $< \alpha$, which is 0.002916602, we reject $H_0$.














